---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dsm2utils

<!-- badges: start -->
<!-- badges: end -->

The goal of dsm2utils is to provide a variety of utilities for working with DSM2 tidefiles. This ranges from reading basic metadata (e.g., start and end datetimes) to extracting flows for a particular (external) channel number.

## Installation

You can install the development version of dsm2utils from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("dougjack/dsm2utils")
```

## Example

This example shows how to obtain the basic metadata stored in a file, hist_v82.h5.
Note: system.file() is used here to obtain the full path to an example tidefile. In your usage, you'll just provide the path to the tidefile on your local machine.

```{r example}
library(dsm2utils)
out <- summarizeTidefile(system.file("extdata", "hist_v82.h5", package="dsm2utils", mustWork=TRUE))
```
